\makeheading{Fan Zhang}

\newlength{\rcollength}\setlength{\rcollength}{2.3in}%

\vspace{-1.4cm}
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}rp{\rcollength}}
 & \url{https://fanzhang.me}\\
 & \email{fanz@cs.cornell.edu} \\
 & 2 West Loop, New York, NY 10044
\end{tabular}


\vspace{2mm}
\Section{Education}
\Subsection{Ph.D. Candidate in Computer Science}{Aug, 2014--present}
\begin{innerlist}
\item[] Advisor: Prof. Ari Juels
\item[] Dept.\ of Computer Science
\item[] Cornell University, Ithaca, NY
\end{innerlist}

\smallskip
\Subsection{B.S. in Electronic Engineering}{Aug, 2010 -- Jul, 2014}
\begin{innerlist}
\item[] Tsinghua University, Beijing, China
\end{innerlist}


\Section{Research Interests}
My research interests center on the security and privacy of decentralized systems, especially those enabled by blockchain protocols and trusted execution environments.

\Section{Industry Adoption}
My research has led to direct industry adoption.
Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} was licensed from Cornell by \href{https://chain.link}{Chainlink} and Ekiden~\cite{DBLP:conf/eurosp/ChengZKHHJJ0S19} is used in \href{https://oasislabs.com}{Oasis Labs}' products. CHURP~\cite{DBLP:journals/iacr/Maram0WLZJS19} is on Oasis Labs product roadmap. DECO~\cite{1909.00938} is under licensing negotiation.


\Section{Awards}
\begin{loneinnerlist}
\item {IBM PhD Fellowship Award}\hfill {2018-2020}
\item {Academic Excellence Scholarship, Tsinghua University, China}\hfill{2013}
\item {National Scholarship, the Ministry of Education of China}\hfill{2012}
\item {Freshman Scholarship, Tsinghua University, China}\hfill{2010}
\end{loneinnerlist}

\Section{Selected Publications}
\vspace{-4mm}

\nocite{*}
\printbibliography[heading=none]


\Section{Employment}
\Subsection{Cornell University}{May, 2011 -- present} \\
Graduate Research Assistant \hfill New York, NY \\[2mm]
%
\Subsection{Oasis Labs}{May, 2017 -- Aug, 2017} \\
Researcher \hfill Berkeley, CA\\[2mm]
%
\Subsection{Security \& Privacy Research, Intel Labs} {Jul, 2017 -- Aug, 2017} \\
Researcher \hfill Hillsboro, OR\\[2mm]
%
\Subsection{Intel Opensource Technology Center (01.org)} {Jun, 2013 -- May, 2014} \\
Intern \hfill Beijing, China

\Section{Teaching Experience}
\begin{loneinnerlist}
\item TA for CS5435: Security and Privacy in the Wild \hfill 2015, Fall
\item TA for CS5300: the Architecture of Large-scale Information Systems \hfill 2015, Spring
\item TA for CS4410: Operating Systems \hfill 2014 Fall
\end{loneinnerlist}

\Section{Invited Talks}
\SubsectionOne{Connecting Blockchains with the Real World}
\begin{innerlist}
\item CISPA-Helmholtz Center for Information Security, Germany. \hfill Nov, 2019
\item ETH Z\"urich, Switzerland.\hfill Oct, 2019
\item IBM Watson Research Center (IBM PhD fellow).\hfill Sep, 2019
\end{innerlist}

\vspace{2mm}
\SubsectionOne{CHURP: Proactive Secret Sharing with Dynamic Committee}
\begin{innerlist}
\item ACM CCS'19, London, UK.\hfill Nov, 2019
\end{innerlist}

\vspace{2mm}
\SubsectionOne{On Trusted Hardware and Blockchain Hybridization}
\begin{innerlist}
\item Northeastern University, Cybersecurity Speaker Series.\hfill Jan, 2019
\item MIT, CSAIL.\hfill Nov, 2018
\item New York University, CS Colloquium.\hfill Oct, 2018
\end{innerlist}

\vspace{2mm}
\SubsectionOne{Paralysis Proof}
\begin{innerlist}
\item ACM AFT 2019, Z\"urich, Switzerland. \hfill Oct, 2019
\item IC3 Retreat, New York City. \hfill May, 2018
\item 5th Bitcoin Workshop, Financial Crypto'18, Curacao. \hfill{Mar, 2018}
\end{innerlist}

\vspace{2mm}
\SubsectionOne{REM}
\begin{innerlist}
\item
USENIX Security'17, Vancouver BC, Canada. \hfill{Aug, 2017}
\end{innerlist}

\vspace{2mm}
\SubsectionOne{Town Crier}
\begin{innerlist}
\item
Silicon Valley Ethereum Meetup, Santa Clara, CA. \hfill{Aug, 2017}
\item
IC3 Retreat, San Francisco, CA. \hfill{Mar, 2017}
\item
CCS'16, Vienna, Austria. \hfill{Oct, 2016}
\item
IC3 Retreat, New York City. \hfill{May, 2016}
\end{innerlist}

\Section{Professional Activity}
\begin{loneinnerlist}
\item {\bf Program Committee}: BITCOIN'18, collocated with Financial Crypto 2018.
\item {\bf Reviewer}: ACM Computing Surveys (2018), Nature Sustainability (2018)
\item {\bf Subreviewer}: USENIX Security (2016), TCC (2019), FC (2019)
\end{loneinnerlist}

\Section{Software Artifacts}
\begin{loneinnerlist}
\item
Town Crier: an Authenticated Data Feed For Smart Contracts \\
\url{https://town-crier.org}

\item
CHURP: Dynamic-Committee Proactive Secret Sharing \\
\url{https://churp.io}

\item
mbedtls-SGX: a SGX-friendly TLS stack (ported from mbedtls)\\
\url{https://github.com/bl4ck5un/mbedtls-SGX}
\end{loneinnerlist}


\Section{Selected Media Coverage}
\begin{loneinnerlist}
%\item {\it MIT Tech Review China}, ``MIT Tech Review China reported on CHURP'', on Mar 27, 2019.
\item {\it MIT Technology Review}, ``Blockchain smart contracts are finally good for something in the real world'', on Nov 19, 2018.
\item {\it Forbes}, ``Cornell's Town Crier Acquired By Chainlink To Expand Decentralized Oracle Network'', on Nov 1, 2018.
\item {\it BitcoinExchangeGuide}, ``Chainlink Blockchain Company Acquires Cornell’s Town Crier to Bolster Native Smart Contract Network'' on Nov 2, 2018.
\item {\it Unhashed}, ``Chainlink Acquires Town Crier, a Hardware-Based Oracle'', on Nov 3, 2018.
\item {\it Forbes}, ``Big Hitter Crypto Funds Pile Into Privacy-Enhanced Smart Contract Startup Oasis Labs'', on Jul 9, 2018.
\item {\it BitcoinMagazine}, ``Cornell IC3 Researchers Propose Solution to Bitcoin's Multisig {\em Paralysis} Problem'', on Jan 19, 2018.
\item {\it IEEE Spectrum}, ``The Ridiculous Amount of Energy It Takes to Run Bitcoin'', on Sep 28, 2017.
\item {\it CoinDesk}, ``Trust Your Oracle? Cornell Launches Tool for Confidential Blockchain Queries'', on May 17, 2017.
\item {\it MIT Technology Review}, ``How Encrypted Weather Data Could Help Corporate Blockchain Dreams Come True'', on May 11, 2017.
\item {\it ETHNews}, ``Town Crier Service Delivers Solid Data To Coders'', on May 11, 2017.
\end{loneinnerlist}
